### 2012-08-02 paper/chemokine.tex
Paper split into Main and Supplement

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=0.4\textwidth]{SystemChart}
\end{center}
\caption{A region of infected tissue of radius $r$ (shaded region $A$) expressing chemokines and inflammatory signals. This region is surrounded by region $B$ which does not have any infected cells and hence does not express either chemokines or inflammatory signals. The $2^{14}$ capillaries (red circles) are distributed evenly throughout the entire lung (region $A$ and $B$).}
\label{fig:systemchart}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=\textwidth]{ModelChart}
\end{center}
\caption{Computational model: Components and state transitions.}
\label{fig:modelchart}
\end{figure}

>>>>

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=0.6\textwidth]{SystemChart}
\end{center}
\caption{A region of infected tissue of radius $r$ (shaded region $A$) expressing chemokines and inflammatory signals. This region is surrounded by region $B$ which does not have any infected cells and hence does not express either chemokines or inflammatory signals. The $2^{14}$ capillaries (red circles) are distributed evenly throughout the entire lung (region $A$ and $B$).}
\label{fig:systemchart}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=\textwidth]{ModelChart}
\end{center}
\caption{A visual representation of the model.  Healthy epithelial cells are infected by virus.  These infected cells secrete more virus after an incubation delay.  T-cells are activated in the lymph node and traverse the bronchial vascular network to the site of infection where they are recruited by inflammatory cytokine.  Once inside the lung tissue, T-cells climb the chemokine gradient and induce apoptosis in infected cells.}
\label{fig:modelchart}
\end{figure}
